Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-15 writeup/gz_hubble_data.tex
Caption of Figure 7. Closes #103.

\begin{figure}
\center
\includegraphics[width=0.50\textwidth]{figures/zeta_mu.png}
\caption{All fits for the vote fraction dropoff parameter $\zeta$ for
$f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface
brightness. This includes only the 37~galaxies with a reasonably bounded range
on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the
function.}
\label{fig:zeta_mu}
\end{figure}

>>>>

\begin{figure}
\center
\includegraphics[width=0.50\textwidth]{figures/zeta_mu.png}
\caption{All fits for the vote fraction dropoff parameter $\zeta$ for
\ffeatures{} in the \ferengi{} galaxies as a function of surface
brightness. This includes only those galaxies with a reasonably bounded range
on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit each
function (37 original galaxies, each artificially redshifted to create a total
of 296~images}
\label{fig:zeta_mu}
\end{figure}
